---
title: "Gender and Leadership in Turbulent Times"
subtitle:  "A Quantitative Analysis of Speeches During COVID-19"
author: "Mariana Arrieta Yanez"
date: "4/15/2021"
output: html_document
---
*I would like to acknowledge Sara Dada and her team for their willingness to share the speech data with me. Their [paper](https://gh.bmj.com/content/6/1/e003910) on political and gender analysis of speeches made by government heads served as the starting point of this project. *
```{r, warning=FALSE, message= FALSE}
library(tidyverse)
library(quanteda)
library(quanteda.dictionaries)
library(quanteda.textmodels)
library(ggplot2)
library(lubridate)
library(rstatix)
library(ggpubr)
library("topicmodels", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
library(ldatuning)
library(RColorBrewer)
```

```{r, warning=FALSE, message= FALSE}
#Load data
df <- read_csv("Speech_data.csv")

#Create vector with the name of the countries in which the leaders are female 
countries_female_leader <- c("Bangladesh", "Bolivia", "Belgium", "Finland", "Germany", "New Zealand", "Norway", "Scotland", "Sint Maarten", "Taiwan")

#Add column that specifies gender
df <- df %>%
  mutate(gender = ifelse(df$country %in% countries_female_leader, "F", "M"))%>%
  mutate(gender = as.factor(gender)) %>%
  drop_na()

#Generate the corpus
speech_corpus <- corpus(df, text_field = "speech", docvars = data.frame(gender =df$gender))

#Create a meaningful document ID
docid <- paste(df$date, 
               df$name, sep = " ")
docnames(speech_corpus) <- docid

df2 <- df %>% group_by(name) %>% mutate(count = n())

```

### 1. Linguistic Features
#### 1.1 Speech length
```{r,warning=FALSE, message= FALSE}
#Subset corpus by gender
speech_f <- corpus_subset(speech_corpus, gender == "F")
speech_m <- corpus_subset(speech_corpus, gender == "M")
#Get number of words per speech and store them in dataframes
speech_f <-as.data.frame(ntoken(speech_f))  %>%
  mutate(gender = "F") %>%
  rename(n_words = 'ntoken(speech_f)')

speech_m <- as.data.frame(ntoken(speech_m)) %>%
  mutate(gender = "M")  %>%
  rename(n_words = 'ntoken(speech_m)')

#Combine both dataframes
word_count_df <- rbind(speech_f, speech_m) %>%
  mutate(gender = as.factor(gender))

#Get the mean for the speechesacross gender
mu_f <- mean(speech_f$n_words)
mu_m <- mean(speech_m$n_words)
mu <- c(mu_f, mu_m)
gender<- c("F", "M")
mu_df <- data.frame(mu, gender) %>%
  mutate(delta= as.factor(gender))

#Plot a histogram to see the cosine similarity score distribution
ggplot(word_count_df, aes(x=n_words, color= gender, fill= gender)) +  
  geom_histogram(aes(y=..density..), position="identity", binwidth = 300, alpha=0.5)+
  geom_density(alpha=0.4)+
  geom_vline(data=mu_df, aes(xintercept=mu, color=gender),
             linetype="dashed")+
  scale_color_manual(values=c("#DA0431", "#56B4E9"))+
scale_fill_manual(values=c("#DA0431", "#56B4E9"), )+
  labs(x="Word Count", y = "Density", fill = "", color = "")+
  annotate("text", x = 1550, y = 0.00070, label = "μ =  1490", angle = 270)+
  annotate("text", x = 1700, y = 0.00070, label = "μ =  1645", angle = 270)+
theme_classic() +
  theme(legend.position="top")

```

#### 1.2 Lexical diversity 
```{r}
#Generate DFMs
speech_dfm_f <- corpus_subset(speech_corpus, gender == "F") %>%
dfm(remove = stopwords("en"))

speech_dfm_m <- corpus_subset(speech_corpus, gender == "M")%>%
dfm(remove = stopwords("en"))

#Get different measures of lexical diversity
tstat_lexdiv_f <- textstat_lexdiv(speech_dfm_f, measure = c("TTR", "CTTR","Maas", "K"))
tstat_lexdiv_m <- textstat_lexdiv(speech_dfm_m, measure = c("TTR", "CTTR","Maas", "K"))
#Lexical diversity
tstat_lexdiv_f %>%
  summarise(across(TTR:K, mean))

tstat_lexdiv_m %>%
  summarise(across(TTR:K, mean))

tstat_lexdiv_df <- as.data.frame(tstat_lexdiv_f) %>%
  select(TTR, Maas) %>%
  mutate(gender = "F")

tstat_lexdiv_df2 <- as.data.frame(tstat_lexdiv_m) %>%
  select(TTR, Maas) %>%
  mutate(gender = "M")

tstat_lexdiv_df <- rbind(tstat_lexdiv_df, tstat_lexdiv_df2)
t.test(TTR ~ gender, data = tstat_lexdiv_df)
t.test(Maas ~ gender, data = tstat_lexdiv_df)

```

#### 1.3 Use of pronouns
```{r}
#Create dictionary with pronouns
myThes <- dictionary(list(I = c("I", "me", "my", "mine", "myself"),
                          We = c("we", "us", "our", "ours", "ourselves"),
                               You = c("you", "your", "yours", "yourself", "yourselves"),
                               They = c("they", "them", "their", "theirs", "themselves")))

#Generate DFMs with the dictionary
pronouns_dfm_f <- corpus_subset(speech_corpus, gender == "F") %>%
dfm(dictionary = myThes) %>%
convert(to = "data.frame")

pronouns_dfm_m <- corpus_subset(speech_corpus, gender == "M")%>%
dfm(dictionary = myThes)%>%
convert(to = "data.frame")

#Get date vector
dates <- df %>%
filter(gender == "F") %>%
select(date)
#Add a date column
pronouns_dfm_f$dates <- dmy(dates$date)

#Pivot longer
pronouns_dfm_f <- pronouns_dfm_f %>%
pivot_longer(!c(doc_id, dates), names_to = "pronouns", values_to = "count") %>%
mutate(gender = "Female Leaders") 
#Repeat for df with men's speeches
dates <- df %>%
filter(gender == "M") %>%
select(date)

pronouns_dfm_m$dates <- dmy(dates$date)

pronouns_dfm_m <- pronouns_dfm_m %>%
pivot_longer(!c(doc_id, dates), names_to = "pronouns", values_to = "count")%>%
mutate(gender = "Male Leaders") 

pronouns_df <- rbind(pronouns_dfm_f, pronouns_dfm_m)%>%
mutate(gender = as.factor(gender))
#Plot the results

ggplot(pronouns_df, aes(x=pronouns, y=count, fill=gender)) + 
    geom_boxplot() +
    facet_wrap(~pronouns, scale="free", labeller = labeller(pronouns = 
    c("I" = "I and its variants",
      "You" = "You and its variants",
      "They" = "They and its variants", 
      "We" = "We and its variants"))) +
  scale_fill_manual(values=c("#DA0431", "#56B4E9"))+
  labs(y= "Pronoun Count", x= "Pronoun and its Variants", fill = "")+
  theme_classic()+
  theme(legend.position="top")
```


```{r}
#T-test
#I
i_df<-pronouns_df %>%
  filter(pronouns == "I") %>%
  select(count, gender)

t.test(count~gender , data =i_df)
#You
you_df<-pronouns_df %>%
  filter(pronouns == "You") %>%
  select(count, gender)

t.test(count~gender , data =you_df)

#We
we_df<-pronouns_df %>%
  filter(pronouns == "We") %>%
  select(count, gender)

t.test(count~gender , data =we_df)
#They
they_df<-pronouns_df %>%
  filter(pronouns == "They") %>%
  select(count, gender)

t.test(count~gender , data =they_df)

#Understand appearances of the word day
kwic(speech_corpus, pattern = "they", valuetype = "fixed", window = 5)
```
### 2. Dictionary Methods
#### 2.1 Sentiment Analysis
```{r, warning=FALSE}

#Collapse corpus into 2 documents
split_dfm <- dfm(speech_corpus, groups = "gender")
# turn word counts into proportions, this accounts for speech length
split_dfm <- dfm_weight(split_dfm, scheme="prop")

#Load dictionary
data(data_dictionary_geninqposneg)

pos.words <- data_dictionary_geninqposneg[['positive']]
neg.words <- data_dictionary_geninqposneg[['negative']]

#Apply Augmented General Inquirer _Positiv_ and _Negativ_  dictionary
sent_dictionary <- dictionary(list(positive = pos.words,
                          negative = neg.words))

sent <- dfm_lookup(split_dfm, dictionary = sent_dictionary)
#Calculate sentiment score
sent <- convert(sent, to= "data.frame") %>%
  rename(gender= doc_id)%>%
  mutate(gender = as.factor(gender)) %>%
  mutate(score = positive - negative)

ggplot(data=sent, aes(x=gender, y=score, fill=gender)) +
  scale_fill_manual(values=c("#DA0431", "#56B4E9"), name = "Gender")+
  geom_bar(stat="identity")+
  labs(title="Sentiment in Speeches Made by Heads of Government", subtitle= "February 27, 2020 - April 16, 2020", x="Gender", y = "Sentiment Score")+
  theme_minimal()

```
#### 2.2 Moral Foundations Dicitionary
```{r}
#Scale dfms
speech_dfm_f_prop <- dfm_weight(speech_dfm_f, scheme  = "prop")
speech_dfm_m_prop <- dfm_weight(speech_dfm_m, scheme  = "prop")
#Moral Foundations Dictionary
data_dictionary_MFD <- data_dictionary_MFD
# Apply dictionary using `dfm_lookup()` function:
dfm_f_mfd <- dfm_lookup(speech_dfm_f_prop, dictionary = data_dictionary_MFD)
dfm_m_mfd <- dfm_lookup(speech_dfm_m_prop, dictionary = data_dictionary_MFD)
#Create dataframe to get the mean of the proportion of words in each category
df_f <- convert(dfm_f_mfd, to ="data.frame")%>%
  select(-doc_id)
#Remove rows that only have zeros
df_f <- df_f[rowSums(df_f[])>0,]
#Get the mean
df_f <- df_f %>%
summarise(across(care.virtue:sanctity.vice, mean)) %>%
pivot_longer(cols= care.virtue:sanctity.vice, names_to = "mean_value") %>%
mutate(gender = "F")
#Create dataframe to get the mean of the proportion of words in each category
df_m <- convert(dfm_m_mfd, to ="data.frame")%>%
  select(-doc_id)
#Remove rows that only have zeros
df_m <- df_m[rowSums(df_m[])>0,]
#Get the mean
df_m <- df_m %>%
summarise(across(care.virtue:sanctity.vice, mean)) %>%
pivot_longer(cols= care.virtue:sanctity.vice, names_to = "mean_value") %>%
mutate(gender = "M")
#Combine both dataframes
df_comb <- rbind(df_f, df_m)
#Transform delta to a categorical variable
df_comb$gender <- as.factor(df_comb$gender)
#Plot the results
p<- ggplot(data=df_comb, aes(x= mean_value, y=value, fill=gender)) +
geom_bar(stat="identity", color="black", position=position_dodge())+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p + scale_fill_manual(values=c("#DA0431", "#56B4E9"))
```

```{r}
#RID  dictionary
data_dictionary_RID <- data_dictionary_RID
RID_prim <- data_dictionary_RID$PRIMARY
RID_emotions <- data_dictionary_RID$EMOTIONS
RID_secondary <- data_dictionary_RID$SECONDARY
#Divide dfm by gender
by_gender_dfm <- speech_corpus %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE) %>%
  tokens_remove(stopwords("en")) %>% #padding prevents the formation of non-sense bigrams
  dfm(groups = "gender", remove = c("st"))

#Scale dfms
speech_dfm_prop <- dfm_weight(by_gender_dfm, scheme  = "prop")

#EMOTION
# Apply dictionary using `dfm_lookup()` function:
dfm_em <- dfm_lookup(speech_dfm_prop, dictionary = RID_emotions)

#Create dataframe to get the mean of the proportion of words in each category by gender
df_em <- convert(dfm_em, to ="data.frame")
df_em <- df_em %>%
  pivot_longer(!doc_id, names_to = "dict_item", values_to = "prop") %>%
  mutate(type="Emotion-based")

#PRIMARY
# Apply dictionary using `dfm_lookup()` function:
dfm_pr <- dfm_lookup(speech_dfm_prop, dictionary = RID_prim)

#Create dataframe to get the mean of the proportion of words in each category by gender
df_pr <- convert(dfm_pr, to ="data.frame")

df_pr <- df_pr %>%
  pivot_longer(!doc_id, names_to = "dict_item", values_to = "prop") %>%
  mutate(type="Image-based")
#SECONDARY
# Apply dictionary using `dfm_lookup()` function:
dfm_sec <- dfm_lookup(speech_dfm_prop, dictionary = RID_secondary)

#Create dataframe to get the mean of the proportion of words in each category by gender
df_sec <- convert(dfm_sec, to ="data.frame")

df_sec <- df_sec %>%
  pivot_longer(!doc_id, names_to = "dict_item", values_to = "prop") %>%
  mutate(type="Concept-based")

#combine
df_comb <- rbind(df_em, df_pr, df_sec)

#Comparisons
dt_result <- df_comb %>% group_by(type) %>% do(tidy(t.test(prop~doc_id, data=.)))

dt_result

ggplot(df_comb, aes(x=type, y=prop, fill=doc_id)) + 
    geom_boxplot() +
    facet_wrap(~type, scale="free") +
  scale_fill_manual(values=c("#DA0431", "#56B4E9"))+
  labs(y= "Proportion of Words", x= "Regressive Imagery Dictionary Categories", fill = "Gender")+
  theme_classic()
```

```{r}
#T-test
#Concept Based
c_df<-df_comb %>%
  filter(type == "Concept-based") %>%
  select(doc_id, prop)

t.test(prop~doc_id , data =c_df)

#Emotion Based
e_df<-df_comb %>%
  filter(type == "Emotion-based") %>%
  select(doc_id, prop)

t.test(prop~doc_id , data =e_df)
```

```{r, out.width = "20%"}
#Collapse corpus into n documents, where n is the number of heads of governments in the dataset
by_leader_dfm <- speech_corpus %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE) %>%
  tokens_remove(stopwords("en")) %>% #padding prevents the formation of non-sense bigrams
  dfm(groups = "name", remove = c("st"))
#Scale dfms
speech_dfm_prop <- dfm_weight(by_leader_dfm, scheme  = "prop")
#RID  dictionary
data_dictionary_RID <- data_dictionary_RID
RID_glory <- data_dictionary_RID$EMOTIONS$GLORY
RID_order <- data_dictionary_RID$PRIMARY$REGR_KNOL$UNKNOW
RID_pas <- data_dictionary_RID$PRIMARY$DEFENSIVE_SYMBOL$PASSIVITY

dict <- dictionary(list(Passivity = RID_pas))

#EMOTION
# Apply dictionary using `dfm_lookup()` function:
dfm_zoom <- dfm_lookup(speech_dfm_prop, dictionary = dict)

#Create dataframe to get the mean of the proportion of words in each category by leader
df_zoom <- convert(dfm_zoom, to ="data.frame")

#Create a gender vector
gender_vect <- df %>% distinct(name, .keep_all = TRUE)

gender_vect <- gender_vect[order(gender_vect$name),]

gender_vect <- gender_vect %>%
select(gender)

df_zoom <- cbind(df_zoom, gender_vect)
  
df_zoom <- df_zoom %>%
  pivot_longer(!c(doc_id,gender), names_to = "type", values_to = "prop") %>%
  mutate(gender = as.factor(gender)) %>%
  select(-doc_id)

#T test to compare differences
dt_result <- df_zoom %>% group_by(type) %>% do(tidy(t.test(prop~gender, data=.)))


ggplot(df_zoom, aes(x=type, y=prop, fill=gender)) + 
    geom_boxplot() +
    facet_wrap(~type, scale="free") +
  scale_fill_manual(values=c("#DA0431", "#56B4E9"))+
  labs(y= "Proportion of Words", x= "Selected RID Sub-categories", fill = "Gender")+
  theme_classic()
```

```{r}
#Generate DFMs
speech_dfm_f <- corpus_subset(speech_corpus, gender == "F") %>%
dfm(remove = stopwords("en"))

speech_dfm_m <- corpus_subset(speech_corpus, gender == "M")%>%
dfm(remove = stopwords("en"))
speech_f <- corpus_subset(speech_corpus, gender == "F")
rel_freq_f <- textstat_frequency(speech_dfm_f)
rel_freq_m <- textstat_frequency(speech_dfm_m)

# Filter the term "RID_pas"
rel_freq_f <- subset(rel_freq_f, feature %in% RID_pas)  

rel_freq_m <- subset(rel_freq_m, feature %in% RID_pas)  

# Apply dictionary using `dfm_lookup()` function:
dfm_zoom <- dfm_lookup(speech_dfm_prop, dictionary = dict)

# Calculate relative frequency by president
freq_weight <- textstat_frequency(dfm_zoom, n = 7, 
                                  groups = dfm_zoom$gender)

ggplot(data = freq_weight, aes(x = nrow(freq_weight):1, y = frequency)) +
     geom_point() +
     facet_wrap(~ group, scales = "free") +
     coord_flip() +
     scale_x_continuous(breaks = nrow(freq_weight):1,
                        labels = freq_weight$feature) +
     labs(x = NULL, y = "Relative frequency")
```



### 3. Wordfish

```{r}
#Collapse corpus into n documents, where n is the number of heads of governments in the dataset
by_leader_dfm <- speech_corpus %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE) %>%
  tokens_remove(stopwords("en"), padding = TRUE) %>% #padding prevents the formation of non-sense bigrams
  tokens_ngrams(n = 1:2) %>% # up to bigrams
  dfm(groups = "name", remove = c("st"))

#Convert dfm to df
by_leader_dfm <- convert(by_leader_dfm, to = "data.frame")
vector <- c()
#Remove words that are only used by ONE leader
for(i in 1:ncol(by_leader_dfm)){
  if( length(unique(by_leader_dfm[,i])) == 2 & (unique(by_leader_dfm[,4])[1] == 0 | unique(by_leader_dfm[,4])[2]==0)){
    vector <- c(vector, i)
  }
}

by_leader_dfm <- by_leader_dfm[ -vector ]
leader_name <- by_leader_dfm$doc_id
#Convert back to dfm
by_leader_dfm <- as.dfm(by_leader_dfm)
#rewrite docnames
docnames(by_leader_dfm) <- leader_name
by_leader_dfm <- dfm_remove(by_leader_dfm, 'doc_id')
# fitting wordfish
wf <- textmodel_wordfish(by_leader_dfm, dir=c(3,2))
#Create dataframe with the results
df_wf <- data.frame(wf$docs, wf$theta, wf$se.theta)
summary(wf)
textplot_scale1d(wf)
# looking at results
sort(predict(wf))


# let's look at the word-level parameters
sw <- data.frame( word=wf$features, beta=wf$beta, psi=wf$psi)
sw <- sw[order(sw$beta),] # discrimination
head(sw, n=60)
tail(sw, n=60)

sw <- sw[order(sw$psi),] # frequency
head(sw, n=60)
tail(sw, n=60)

# plotting both into an "Eiffel tower" plot
plot(wf$beta, wf$psi, type = "n", 
     xlab = "Word discrimination parameters", 
     ylab = "Word frequency parameters")
text(wf$beta, wf$psi, wf$features, col = "grey80", cex = .5)

textplot_scale1d(wf, margin = "features", 
                 highlighted = c("tremendous", "hopefully", 
                                 "regulation", "lockdown", "people", "health", "happy", "social_welfare",
                                  "enough_ventilators", "protect", "emergency", "waiver", "restriction", "alcoholic"))
```
#This graph tells us something about the extremes, but we don't know much about the people in the middle 

```{r}
#Create a gender vector
gender_vect <- df %>% distinct(name, .keep_all = TRUE)

gender_vect <- gender_vect[order(gender_vect$name),]

gender_vect <- gender_vect %>%
select(gender)

#Combine the gender vector with the wordfish dataframe
df_wf <- cbind(df_wf, gender_vect) %>%
  mutate(gender = as.factor(gender))

#Order the ideology data frame by the speech score
df_wf <- df_wf[order(df_wf$wf.theta),]

#Create an equally spaced sequence for the y-axis of the points
my_seq <- seq(0.05625,1.15, by = 0.05625)
#create the y_axis variable
df_wf <- df_wf %>%
  mutate(y_axis = my_seq) %>%
  mutate(standard_error = wf.se.theta*1.6)

fem_med <- df_wf %>%
  filter(gender== "F")%>%
   summarise(wf.theta = median(wf.theta))

male_med <- df_wf %>%
  filter(gender== "M")%>%
   summarise(wf.theta = median(wf.theta))

ggplot(df_wf, aes(x=wf.theta, fill=gender, color= gender)) + 
  #Plot distributions
  geom_density(alpha=.3, linetype = "blank")+
  #Plot Senator's twscore
  geom_point(data=df_wf, 
             aes(x=wf.theta, y=y_axis, color = gender, fill= gender),
             size= 0.2)+
  #plot the range of the senator's twscore
  geom_pointrange(data=df_wf, mapping=aes(x=wf.theta, y= y_axis, xmin=wf.theta - standard_error, xmax= wf.theta + standard_error, color = gender, fill= gender), width=0.15, size= 0.2)+ 
  #names that goes to the left
  geom_text( data= df_wf, aes(x=wf.theta , y= y_axis, label = wf.docs, color = gender, fill = gender),
            size= 2,
            vjust = 0, nudge_y = 0.02,
            check_overlap = T) +
  scale_fill_manual(values=c("#DA0431", "#56B4E9"))+
  scale_color_manual(values=c("#DA0431", "#56B4E9"))+
  theme_classic()+
  #Remove gap between x-axis and the plot
  #scale_x_continuous(limits = c(-3,2.5), expand = c(0, 0)) +
  labs(title="",
       x ="Position on latent ideological scale")+
  #remove y-axis
   theme(legend.position = "none",
        axis.line.y =element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(), 
        axis.line.x = element_blank(), 
        #panel.grid = element_blank(),
        panel.border = element_blank(), 
        plot.title = element_text(color="black", size=11, face="bold"))



```
```{r}
library("topicmodels", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
library(seededlda)

speeches_dfm <- speech_corpus %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE) %>%
  tokens_remove(stopwords("en"), padding = TRUE) %>% #padding prevents the formation of non-sense bigrams
  tokens_ngrams(n = 1:2) %>% # up to bigrams
  dfm( remove = c("st", "st_martin"), stem = TRUE, tolower = TRUE)
#Create dictionary with prnouns
myThes <- dictionary(list(Economy = c("bankruptcy", "econom*", "market*", "money", "bank*", "stock*", "bond*", "industry, company", "shop*", "unemploy*", "furlough"),
                          Social_Welfare = c("alcohol*", "welfare", "domestic_violence", "violence", "mental_health", "vulnerable", "pregnant", "elder*"),
                               Nationalism = c("self-reliant", "nation*", "proud", "foreign_country", "independent"),
                               Cooperation = c("international_cooperation", "cooperation", "solidarity", "help"), 
                          Emotional = c("war*", "battle*", "fight", "enem*")))

tmod_slda <- textmodel_seededlda(speeches_dfm, dictionary = myThes)
terms(tmod_slda, 20)
tmod_slda

```


```{r}
#Get the most maximum gamma for a given document. That is, the most likely topic for a given SPEECH

#Create name and gender vecto
df_name_gender <- df %>%
  select(name, gender)
#Get theta from LDA
df_theta <- as.data.frame(tmod_slda[["theta"]])
#COmbine both dfs
df_theta <- cbind(df_theta, df_name_gender)%>%
  relocate(name)
#Mean value df 
df_theta <- df_theta%>%
    group_by(name) %>%
    mutate(econ_mean= mean(Economy)) %>%
    mutate(sw_mean= mean(Social_Welfare)) %>%
  mutate(nat_mean = mean(Nationalism))%>%
  mutate(coop_mean = mean(Cooperation)) %>%
  mutate(emo_mean = mean(Emotional))
df_theta <- df_theta%>%
  distinct(name, .keep_all = TRUE) %>%
  select(-c(Economy, Social_Welfare, Nationalism, Cooperation, Emotional))

df_theta <- df_theta %>%
  pivot_longer(!c(name, gender), names_to = "topic", values_to = "prop")

ggplot(df_theta, aes(fill=topic, y=prop, x=topic)) + 
    geom_bar(position="dodge", stat="identity") +
  facet_wrap(~name) +
  theme_bw()+
  scale_fill_manual(name = "Topic", labels = c("Cooperation", "Economy","Emotional Appeals" , "Nationalism", "Social Welfare"), values = c("#fdd760", "#ec3e4b", "#018f97", "#e98d20","#ede1b9"))+
  scale_x_discrete(labels=c("C", "E", "EA","N", "SW"))+
  labs(x = "", y= "Average Probability of Topic Prevalence Across Speeches")+
  theme(legend.position="top")
```


```{r}
#Get the most maximum gamma for a given document. That is, the most likely topic for a given SPEECH
df_theta2 <- as.data.frame(tmod_slda[["theta"]])

df_theta2 <- df_theta2 %>%
  rownames_to_column(var = "rowname") %>%
  cbind(df_name_gender) %>%
  select(-c(rowname, name))%>%
  relocate(gender)

#Pivot longer
df_theta2 <- df_theta2 %>%
  pivot_longer(!gender, names_to = "topic", values_to = "prop")

#T test to compare differences
dt_result <- df_theta2 %>% group_by(topic) %>% do(tidy(t.test(prop~gender, data=.)))

#Emotion Based
e_df<-df_comb %>%
  filter(type == "Emotion-based") %>%
  select(doc_id, prop)

t.test(prop~doc_id , data =e_df)

ggplot(df_theta2, aes(x=topic, y=prop, fill=gender)) + 
    geom_boxplot() +
    facet_wrap(~topic, scale="free") +
  scale_fill_manual(values=c("#DA0431", "#56B4E9"))+
  labs(y= "Probability of Topic Prevalence Across Speeches", x= "Topic", fill = "Gender")+
  theme_classic()
```

